---
title: "p8105_hw5_zw2541"
author: "Zixu_Wang"
date: "11/4/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Problem 1

### Read and clean the data

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.

```{r}
file_names = list.files(path = "./data_1")


read_and_tidy = function(file_names){
     read.csv(str_c("./data_1/", file_names)) %>% 
     janitor::clean_names() %>% 
     as.data.frame() %>% 
     mutate(group = file_names) %>% 
     select(group, everything())
}

study_data = map(file_names, read_and_tidy) %>% 
  bind_rows() %>% 
  gather(key = week, value = data, week_1:week_8) %>% 
  mutate(group = str_replace(group, ".csv", "")) %>% 
  separate(group, into = c("group", "id"), sep = "_") %>% 
  mutate(week = str_replace(week, "week_", ""))
```

### Spaghetti plot

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
study_data %>%
  ggplot(aes(x = as.numeric(week), y = data, color = id)) +
  geom_line() +
  facet_grid(~ group) +
  labs(
    title = "Observations on Each Subject over Time",
    x = "Week",
    y = "Value",
    caption = "Data from a longitudinal study") +
  theme(legend.position = "bottom")
```

## Problem 2

### Read and clean the data

```{r}
homicides_data = 
  read.csv("./data_2/homicide-data.csv") %>% 
  janitor::clean_names() 
```

### Describe the raw data

Create a city_state variable (e.g. "Baltimore, MD") and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is "Closed without arrest" or "Open/No arrest").

```{r}
summarize_homicides = 
  homicides_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  select(-city, -state) %>% 
  group_by(city_state) %>% 
  summarize(n_homicides = n(),
            n_unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))

summarize_homicides
```

### prop.test of Baltimore, MD

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore =
  summarize_homicides %>% 
  filter(city_state == "Baltimore, MD") 

  prop.test(baltimore$n_unsolved_homicides, baltimore$n_homicides) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
```

The estimated proportion is 0.646 and confidence intervals is (0.628, 0.663).

### Run prop.test for each of the cities

```{r}
test_result = map2(.x = summarize_homicides$n_unsolved_homicides, 
                  .y = summarize_homicides$n_homicides, 
                  ~prop.test(.x, .y))

pull_result = function(test_result){
  test_result %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
}

tidy_result = map(.x = test_result, ~pull_result(.x)) %>% 
  bind_rows() %>% 
  mutate(city_state = summarize_homicides$city_state) %>% 
  select(city_state, everything()) %>% 
  mutate(city_state = forcats::fct_reorder(city_state,estimate))

tidy_result
```

### Create the plot of estimates and CIs for each city 

```{r}
tidy_result %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, size = 6)) +
  labs(
    title = "Estimates and CIs for each city",
    x = "City, State",
    y = "Estimates(CIs)",
    caption = "Data from the Washington Post")
```

